### 2019-07-23 report/MSc_Report.tex
report correction

\thispagestyle{empty}
\begin{center}
  \vspace*{6cm}{\bfseries\Huge
  Publication Bias in the Cochrane \vspace{3mm} Database of Systematic Reviews
  }
  \vfill
  \rm

@@

Studies get more attention and are more likely to be published, read and cited if they are implying large effects. Studies with no evidence for an effect are less likely to get published. This generates a bias called ``publication bias'', which distorts the view of the evidence for an effect. Recently, publication bias has been identified as one of the major concerns in irreproducible research \citep{Bishop.2019}. The issue has been pin-pointed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}). In medical research, clinical trials study the efficacy of therapies and drugs. The gold standard in such intervention studies are randomized, (placebo) controlled, trials (RCTs). Results from such clinical studies influence the treatment of patients in daily clinical practice. The results from multiple intervention studies are summarized in meta-analyses and reflect the overall evidence for a treatment effect. Summarized treatment effects and uncertainities should be more robust and reliable. Publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm. \\
There is extensive literature on publication bias in meta-analyses, e.g. (\citet{pb.clinicalscience.2013}, %\citet{Hopewell02}, 
\citet{grey.literature.4}, \citet{grey.literature.3}, \citet{grey.literature.2}). 
All authors agree in that the exclusion of unpublished results in meta-analyses is responsible for overestimation of treatment effects. Although there are policies that make it mandatory to make accessible all study results \citep{fda}, it is not clear if the situation has improved yet.\\
The Cochrane Organisation has specialized on systematic reviews of healthcare interventions. Researchers that write a systematic review collect data across studies, review them and try to provide up-to-date information about specific treatment efficacies \citep{cochrane.handbook}. By extensive literature scrutinization, they try to circumvent the issue of publication bias. Earlier research however suggests that the efforts are only partially succesful, and that there still is publication bias within the reviews (\citet{Egger}, \citet{Ioannidis2007}, \citet{kicinsky}, \citet{vanAert.2019}). In this publications, the results of a part of the Cochrane Database of systematic reviews is analysed with small study effect tests or bayesian hierarchical selection models \citep{kicinsky}. They all find moderate to large evidence for publication bias in the Database. A more thorough discussion of their methods and results will follow in chapter \ref{ch:Discussion}. None of the research so far has estimated the amount and impact of publication bias on meta-analytical findings thoroughly and with the most suitable methods. Also, the results are often presented in the form of dichotomized hypothesis tests, a practice known to contribute to publication bias itself (cite sb).\\
The aim of this thesis is to use prevailed methods to detect publication bias, and make use of the full amount of data that the Cochrane Organisation provides. At the end, an up-to-date estimate of the prevalence of publication bias in the data shall be given, as well as its implications regarding the effect sizes of the treatments. To achieve this, methods to detect and adjust for publication bias in meta-analysis are applied on the data.

\subsection{Analysing publication bias}
There are multiple ways to assess the amount of publication bias. For instance, one can follow studies and control if they are getting published depending on their findings \citep{publication.fate}. One often finds that positive findings (\ie large effects) are reported and published more often (see also an example in social sciences: \citet{social.sciences.publication.bias}). Another way is to compare results in study registries with results published in journals (\eg \citet{pb.clinicalscience.2013}). Again one finds systematic differences between published and unpublished results. \\
A third way is to assess the so-called small study effect in a meta-analysis, that is, a systematic difference between effects of large and small studies. Evidence for small study effects can oftentimes be interpreted as evidence for publication bias \citep{Egger}. The underlying rational is that journal editors are guided by two simple rules (\citet{excess.significance}, \citet{ioannidis.2019}): 
\begin{itemize}
\item Publish new and trend-setting findings that lead to many citations, increasing the journal impact factor (JIF).
\item Publish large trials that are likely to set the standard for a given scientific question, again to increase the JIF.
\end{itemize}
This then leads to the so-called asymmetry in the funnel plot of published studies; small studies show larger effect sizes than larger studies do. By means of simple linear regression, one can investigate how much evidence there is for this asymmetry. For illustration purposes, a meta-analysis with large funnel plot asymmetry is shown %\citep{pre.eclampsia}:

@@

\end{knitrout}
\end{figure}

@@

@@

\begin{align}
\theta &= \beta_0 + \beta_1 \se + \epsilon, & \epsilon \sim N(0, w^{-1}\sigma^2) \label{eq:egger.plot}
\end{align}

@@

After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before in the simple linear regression framework. Now we have basically two possible estimates at hand:
\begin{itemize}
\item $\beta_0$ the treatment effect without any influence of study precision with standard error $s_{\beta_0}$
\item $\beta_0 + \beta_1 \tau$ the treatment effect of a hypothetical study with infinite precision, corresponding standard error $s_{\beta_0} + s_{\beta_1}$
\end{itemize}

@@

\subsection{Structure and Content}
The dataset consists of 6353 systematic reviews from the Cochrane Library with 70662 studies and 744717 results. The results all stem from comparisons of a healthcare interventions or treatments to a reference. The reference may be a placebo control group or a other intervention or treatment. A result can not only be about efficacy of the treatments, but also about safety (adverse effects).\\
In Table \ref{barbiturate.row}, two results from a systematic review about barbiturates are shown as they are given in the dataset. As can be seen, further specifications are provided by the variables in the columns. \\
The \texttt{comparison.name} variable specifies \textit{what kind} of treatments or interventions are compared, the \texttt{outcome.name} variable \textit{how} it is compared, and the \texttt{subgroup.name} variable (not indicated in table) \textit{if and to what experimental subgroup} the result belongs. \\
The result is of a binary type, and the counts of events in the treatment group are in \texttt{events1} and of the control group in \texttt{events2} and the total number of participants are given in columns \texttt{total1} and \texttt{total2}. As can be seen, events denote here "death at the end of follow-up".

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Sun Jul 14 14:23:32 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lllrrrr}
  \hline
study.name & comparison.name & outcome.name & events1 & total1 & events2 & total2 \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11 & 41 & 11 & 41 \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14 & 27 & 13 & 26 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Example of two results as given in the dataset. Events denotes the count of events in the treatment group while Events c the count of events in the group compared to. Further descriptive variables have been ommitted} 
\label{barbiturate.row}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Sun Jul 14 14:23:32 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
study.name & comparison.name & outcome.name \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
   \hline
\end{tabular}
\endgroup
\caption{Barbiturate and head injury review. In the columns, study names, comparison and outcome measure of the results are given} 
\label{barbiturates}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Sun Jul 14 14:23:32 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lr}
  \hline
  \hline
Neither means nor standard deviations (CONT) & 775 \\ 
  Zero participants in one group & 15162 \\ 
  Missing study publication year & 7942 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Number of missing variables and measurements in the dataset} 
\label{missing}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Sun Jul 14 14:23:32 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lrr}
  \hline
Outcome measure & n & Percentage \\ 
  \hline
RR & 361902 & 48.6\% \\ 
  MD & 164920 & 22.1\% \\ 
  OR & 72012 & 9.7\% \\ 
  SMD & 70717 & 9.5\% \\ 
  PETO\_OR & 39710 & 5.3\% \\ 
  RD & 11068 & 1.5\% \\ 
  Hazard Ratio & 8054 & 1.1\% \\ 
  Odds Ratio & 4055 & 0.5\% \\ 
  other & 12279 & 1.6\% \\ 
   \hline
\end{tabular}
\endgroup
\caption{Frequencies of outcome measures among results. n denotes the total number 
             of results with the outcome measure and percentage the percentage of the outcome measure,} 
\label{outcome.measure.frequencies}
\end{table}

The sample sizes among results vary to some extent. There are 5\% of treatment group sample sizes that are smaller than 9, 95\% smaller than 510. The first quartile is 23, the median 48, the mean 256.71 and the third quartile 116. The large difference between median and mean is caused by very large groups with over 2,000,000 participants. Analogously, the quantiles of the total sample size are: 5\% quantile = 17, first quartile = 44, median = 94, third quartile = 223 and 95\% = 983. The mean is 623.16. \\
There are 518 reviews with five or fewer results. The 5\% and 95\% quantiles are 4 and 447. The mean and median number of results per review are 13.6 and 8, and the quartiles are 16 and 109. Similarly, the number of reviews with a maximum of two studies included is 1039, the mean study number is 13.6, the median 8 and the interquartile range 4 and 16 and the 95\% quantile 45. The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citet{largest.review} 
which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1,497 results in total.\\
For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome. The studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis. This distinction is also used by the Cochrane Organization itself, \ie the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
The size of a meta-analysis denotes how many results are included in a group. Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results.

@@

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Sun Jul 14 14:23:32 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lrr}
  \hline
n & Number of groups & Cumulative sum of groups \\ 
  \hline
1 & 143375 & 268903 \\ 
  2 & 45459 & 125528 \\ 
  3 & 23232 & 80069 \\ 
  4 & 14184 & 56837 \\ 
  5 & 9493 & 42653 \\ 
  6 & 6449 & 33160 \\ 
  7 & 4583 & 26711 \\ 
  8 & 3412 & 22128 \\ 
  9 & 2585 & 18716 \\ 
  10 & 2046 & 16131 \\ 
  11 & 1524 & 14085 \\ 
  12 & 1197 & 12561 \\ 
  13 & 1022 & 11364 \\ 
  14 & 785 & 10342 \\ 
  15 & 9557 & 9557 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Number and cumulative number of groups with meta-analysis size n.} 
\label{repr.groups}
\end{table}

@@

\subsection{Newly Introduced Variables}
Some new variables are added to the obtained dataset:
\begin{itemize}
\item \texttt{outcome.measure.new}: Outcome measure specifications given in \texttt{outcome.measure} were standardized whenever they were supposed to denote the same outcome measure. An example would be the formally different notations for odds ratios: ``Odds Ratio'', ``odds ratio'', ``OR'', which were all denoted as ``Odds Ratio''.
% \item \texttt{outcome.flag}: A simplification of \texttt{outcome.measure.new}. The outcome.flag ``bin'' indicates if \texttt{outcome.measure.new} is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''. ``cont'' is equivalent to \texttt{outcome.measure.new} equal to "Std. Mean Difference'' or ``Mean Difference''. ``surv'' equal to ``Hazard Ratio'' and ``rate'' equal to ''Rate Ratio'' or ``Rate Difference''.
\item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.flag ``bin''.
\item \texttt{smd} and \texttt{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.flag ``cont''. 
% If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.new} was equal to ``Std. Mean Difference'', it was set equal to \texttt{effect} (and \texttt{var.smd} equal to \texttt{se} squared, $n$ =  length(inpute.given.ind)).
\item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.flag ``bin''.
\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.flag ``bin'') or $g$ (for outcome.flag ``cont'') to $r$ transformation.
\item \texttt{z} and \texttt{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.flag ``cont'' or Wald test for outcome.flag ``bin''.
\item \texttt{events1c} and \texttt{events2c}: Correction of \texttt{events1} and \texttt{events2} zero event counts or event counts = patient number. When no events occurred, 0.5 was added, and when all patients experienced the event, 0.5 was subtracted. When one of \texttt{events} had zero counts while the other had maximum counts, no adjustment occurred.
\item \texttt{meta.id}: Meta-analysis ID variable to uniquely identify any potential meta-analysis in the dataset. Consistent to what has been discussed before, all results that share a common comparison, outcome and subgroup (optional, subgroups not given in any case) may be combined in a meta-analysis.
\item \texttt{se.new}: Depending on \texttt{outcome.flag}, \texttt{se.new} is equal to the square-root of \texttt{var.lrr} (\texttt{outcome.flag} = \texttt{DICH}), square-root of \texttt{var.smd} (\texttt{CONT})
or \texttt{se} (\texttt{IV}).
% \item \texttt{}:
\end{itemize}

@@

\begin{figure}
\begin{center}
\tikzstyle{block} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=2.5em]
\tikzstyle{btw} = [rectangle, node distance=0cm, minimum height =2em, fill= white]
\tikzstyle{ublock} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=4em, text width = 10em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{final} = [rectangle, draw, fill=red!20, text centered, rounded corners, minimum height=2.8em]

\begin{tikzpicture}[node distance = 2cm, auto]
    % Place nodes
        \node [final] (1) {Inital dataset: 
    6,353 reviews,
    70,662 studies,
    744,717 results};

    \node [block, below of=1, node distance=2.2cm] (2) {
    6,324 reviews,
    69,873 studies,
    734,951 results};

    \node [block, below of=2, node distance=2.2cm] (3) {
    1,262 reviews,
    29,109 studies,
    208,391 results,
    11,463 meta-analyses};

    \node [block, below of=3, node distance=2.2cm] (4) {
    1,241 reviews,
    28,698 studies,
    196,539 results,
    10,830 meta-analyses};

    \node [block, below of=4, node distance=2.2cm] (5) {
    1,157 reviews,
    26,590 studies,
    162,298 results,
    8,575 meta-analyses};

>>>>

\thispagestyle{empty}
\begin{center}
  \vspace*{6cm}{\bfseries\Huge
  Statistical Assessment and Adjustment of Publication Bias in the Cochrane Database of Systematic Reviews
  }
  \vfill
  \rm

@@

Studies get more attention and are more likely to be published, read and cited if they are implying significant effects. Studies with no evidence for an effect are less likely to get published. This generates a bias called ``publication bias'', a distorted view of the evidence for an effect. Recently, publication bias has been identified as one of the major concerns in irreproducible research \citep{Bishop.2019}. The issue has been discussed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}). \\
In medical research, clinical trials study the efficacy of therapies and drugs. The gold standard in such intervention studies are randomized, (placebo) controlled, trials (RCTs). Results from such clinical studies influence the treatment of patients in daily clinical practice. The results from multiple intervention studies are However, publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm. \\
There are multiple ways to assess the amount of publication bias. For instance, one can follow studies and control if they are getting published depending on their findings \citep{publication.fate}. One often finds that positive findings (\ie large effects) are reported and published more often (see also an example in social sciences: \citet{social.sciences.publication.bias}). Another way is to compare results in study registries with results published in journals (\eg \citet{pb.clinicalscience.2013}). Again one finds systematic differences between published and unpublished results. \\
A third way is to assess the so-called small study effect in a meta-analysis, that is, a systematic difference between effects of large and small studies. Evidence for small study effects can oftentimes be interpreted as evidence for publication bias \citep{Egger}. The underlying rational is that journal editors are guided by two simple rules (\citet{excess.significance}, \citet{ioannidis.2019}): 
\begin{itemize}
\item Publish new and trend-setting findings that lead to many citations, increasing the journal impact factor (JIF).
\item Publish large trials that are likely to set the standard for a given scientific question, again to increase the JIF.
\end{itemize}
This then leads to the asymmetry in the funnel plot of published studies; small studies show larger effect sizes than larger studies do. A funnel plot allows visual inspection of small study effects by plotting the effects against their standard error. For illustration purposes, one meta-analysis with large funnel plot asymmetry and one with no asymmetry is shown in Figure \ref{small.study.effect.example}. %\citep{pre.eclampsia}: 
By means of simple linear regression, one can investigate how much evidence there is for this asymmetry.

@@

\end{knitrout}
\caption{Funnel plots of two meta-analyses: On the left, the improvement in depression syndroms after application of tricyclic antidepressants is compared to placebo. The meta-analysis on the right measures the occurence of intracranial haemoerrhage by CT after application of any anti-thrombolytic agent. All studies are RCT's.}
\label{small.study.effect.examples}
\end{figure}

@@

\section{Aim of the study}

There is extensive literature on publication bias in meta-analyses, e.g. (\citet{pb.clinicalscience.2013}, %\citet{Hopewell02},
\citet{grey.literature.4}, \citet{grey.literature.3}, \citet{grey.literature.2}).
The authors agree on that the exclusion of unpublished results in meta-analyses is responsible for overestimation of treatment effects. Although there are policies that make it mandatory to make all study results publicly accessible \citep{fda}, it is not clear if the situation has improved yet.\\
The Cochrane Organisation has specialized on systematic reviews of healthcare interventions. Researchers that write a systematic review collect data across studies, review them and try to provide up-to-date information about specific treatment efficacies \citep{cochrane.handbook}. By extensive literature scrutinization, they try to circumvent the issue of publication bias. Earlier research however suggests that the efforts are only partially succesful, and that there still is publication bias within the reviews (\citet{Egger}, \citet{Ioannidis2007}, \citet{kicinsky}, \citet{vanAert.2019}). In these publications, Cochrane systematic reviews is analysed with methods to detect publication bias, for example small study effect tests or bayesian hierarchical selection models \citep{kicinsky}. They all find moderate to large evidence for publication bias in the Database. Their results will be compared to the results of this study in the last chapter.\\
None of the research so far has estimated the amount and impact of publication bias on meta-analytical findings thoroughly and with the most suitable methods. Also, the results are ironically often presented in the form of dichotomized hypothesis tests, a practice that is partly responsible for publication bias.\\
The aim of this thesis is to use prevailed methods to detect publication bias, and make use of the full amount of data that the Cochrane Organisation provides. At the end, an up-to-date estimate of the prevalence of publication bias in the data shall be given, as well as its implications regarding the effect sizes of the treatments. To achieve this, methods to detect and adjust for publication bias in meta-analysis are applied on the data.

@@

\begin{align}
\theta &= \beta_0 + \beta_1 \se + \epsilon, & \epsilon \sim N(0, w^{-2}\sigma^2) \label{eq:egger.plot}
\end{align}

@@

After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before in the simple linear regression framework. Now we have basically two possible estimates at hand:
\begin{itemize}
\item $\beta_0$ the treatment effect without any influence of study precision with standard error $s_{\beta_0}$
\item $\beta_0 + \beta_1 \tau$ the treatment effect of a hypothetical study with infinite precision, corresponding standard error $\se = s_{\beta_0} + s_{\beta_1}$
\end{itemize}

@@

\subsection{Structure and Content}
The dataset consists of 6354 systematic reviews from the Cochrane Library with 70662 studies and 744720 results. The results all stem from comparisons of a healthcare interventions or treatments to a reference. The reference may be a placebo control group or a other intervention or treatment. A result can not only be about efficacy of the treatments, but also about safety (adverse effects).\\
In Table \ref{barbiturate.row}, two results from a systematic review about barbiturates are shown as they are given in the dataset. As can be seen, further specifications are provided by the variables in the columns. \\
The \texttt{comparison.name} variable specifies \textit{what kind} of treatments or interventions are compared, the \texttt{outcome.name} variable \textit{how} it is compared, and the \texttt{subgroup.name} variable (not indicated in table) \textit{if and to what experimental subgroup} the result belongs. \\
The result is of a binary type, and the counts of events in the treatment group are in \texttt{events1} and of the control group in \texttt{events2} and the total number of participants are given in columns \texttt{total1} and \texttt{total2}. As can be seen, events denote here "death at the end of follow-up".

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Jul 23 08:53:36 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lllrrrr}
  \hline
study.name & comparison.name & outcome.name & events1 & total1 & events2 & total2 \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11 & 41 & 11 & 41 \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14 & 27 & 13 & 26 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Example of two results as given in the dataset. Events denotes the count of events in the treatment group while Events c the count of events in the group compared to. Further descriptive variables have been ommitted} 
\label{barbiturate.row}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Jul 23 08:53:36 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
study.name & comparison.name & outcome.name \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
   \hline
\end{tabular}
\endgroup
\caption{Barbiturate and head injury review. In the columns, study names, comparison and outcome measure of the results are given} 
\label{barbiturates}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Jul 23 08:53:36 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lr}
  \hline
  \hline
Neither means nor standard deviations (CONT) & 775 \\ 
  Zero participants in one group & 15162 \\ 
  Missing study publication year & 7942 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Number of missing variables and measurements in the dataset} 
\label{missing}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Jul 23 08:53:36 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lrr}
  \hline
Outcome measure & n & Percentage \\ 
  \hline
RR & 361902 & 48.6\% \\ 
  MD & 164923 & 22.1\% \\ 
  OR & 76067 & 10.2\% \\ 
  SMD & 70717 & 9.5\% \\ 
  PETO\_OR & 39710 & 5.3\% \\ 
  RD & 11068 & 1.5\% \\ 
  Hazard Ratio & 8054 & 1.1\% \\ 
  Rate Ratio & 3724 & 0.5\% \\ 
  other & 8555 & 1.1\% \\ 
   \hline
\end{tabular}
\endgroup
\caption{Frequencies of outcome measures among results. n denotes the total number 
             of results with the outcome measure and percentage the percentage of the outcome measure,} 
\label{outcome.measure.frequencies}
\end{table}

The sample sizes among results vary to some extent. There are 5\% of treatment group sample sizes that are smaller than 9, 95\% smaller than 510. The first quartile is 23, the median 48, the mean 256.71 and the third quartile 116. The large difference between median and mean is caused by very large groups with over 2,000,000 participants. Analogously, the quantiles of the total sample size are: 5\% quantile = 17, first quartile = 44, median = 94, third quartile = 223 and 95\% = 983. The mean is 623.15. \\
There are 519 reviews with five or fewer results. The 5\% and 95\% quantiles are 4 and 447. The mean and median number of results per review are 13.6 and 8, and the quartiles are 16 and 109. Similarly, the number of reviews with a maximum of two studies included is 1040, the mean study number is 13.6, the median 8 and the interquartile range 4 and 16 and the 95\% quantile 45. The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citet{largest.review} 
which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1,497 results in total.\\
For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome. The studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis. This distinction is also used by the Cochrane Organization itself, \ie the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
The size of a meta-analysis denotes how many results are included in a group. Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results.

@@

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Jul 23 08:53:36 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lrr}
  \hline
n & Number of groups & Cumulative sum of groups \\ 
  \hline
1 & 143378 & 268906 \\ 
  2 & 45459 & 125528 \\ 
  3 & 23232 & 80069 \\ 
  4 & 14184 & 56837 \\ 
  5 & 9493 & 42653 \\ 
  6 & 6449 & 33160 \\ 
  7 & 4583 & 26711 \\ 
  8 & 3412 & 22128 \\ 
  9 & 2585 & 18716 \\ 
  10 & 2046 & 16131 \\ 
  11 & 1524 & 14085 \\ 
  12 & 1197 & 12561 \\ 
  13 & 1022 & 11364 \\ 
  14 & 785 & 10342 \\ 
  15 & 9557 & 9557 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Number and cumulative number of groups with meta-analysis size n.} 
\label{repr.groups}
\end{table}

@@

\subsection{Newly Introduced Variables}
Some new variables are added to the obtained dataset:
\begin{itemize}
\item \texttt{outcome.measure.merged}: Outcome measure specifications given in \texttt{outcome.measure} were standardized whenever they were supposed to denote the same outcome measure. An example would be the formally different notations for odds ratios: ``Odds Ratio'', ``odds ratio'', ``OR'', which were all denoted as ``Odds Ratio''.
% \item \texttt{outcome.flag}: A simplification of \texttt{outcome.measure.merged}. The outcome.flag ``bin'' indicates if \texttt{outcome.measure.merged} is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''. ``cont'' is equivalent to \texttt{outcome.measure.merged} equal to "Std. Mean Difference'' or ``Mean Difference''. ``surv'' equal to ``Hazard Ratio'' and ``rate'' equal to ''Rate Ratio'' or ``Rate Difference''.
\item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.flag ``bin''.
\item \texttt{smd} and \texttt{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.flag ``cont''. 
% If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.merged} was equal to ``Std. Mean Difference'', it was set equal to \texttt{effect} (and \texttt{var.smd} equal to \texttt{se} squared, $n$ =  length(inpute.given.ind)).
\item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.flag ``bin''.
\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.flag ``bin'') or $g$ (for outcome.flag ``cont'') to $r$ transformation.
\item \texttt{z} and \texttt{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.flag ``cont'' or Wald test for outcome.flag ``bin''.
\item \texttt{events1c} and \texttt{events2c}: Correction of \texttt{events1} and \texttt{events2} zero event counts or event counts = patient number. When no events occurred, 0.5 was added, and when all patients experienced the event, 0.5 was subtracted. When one of \texttt{events} had zero counts while the other had maximum counts, no adjustment occurred.
\item \texttt{meta.id}: Meta-analysis ID variable to uniquely identify any potential meta-analysis in the dataset. Consistent to what has been discussed before, all results that share a common comparison, outcome and subgroup (optional, subgroups not given in any case) may be combined in a meta-analysis.
\item \texttt{se.new}: Depending on \texttt{outcome.flag}, \texttt{se.new} is equal to the square-root of \texttt{var.lrr} (\texttt{outcome.flag} = \texttt{DICH}), square-root of \texttt{var.smd} (\texttt{CONT})
or \texttt{se} (\texttt{IV}).
% \item \texttt{}:
\end{itemize}

@@

\begin{figure}
\begin{center}
\tikzstyle{block} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=2.3em]
\tikzstyle{btw} = [rectangle, node distance=0cm, minimum height =1.8em, fill= white]
\tikzstyle{ublock} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=4em, text width = 10em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{final} = [rectangle, draw, fill=red!20, text centered, rounded corners, minimum height=2.8em]

\begin{tikzpicture}[node distance = 2cm, auto]
    % Place nodes
        \node [final] (1) {Inital dataset: 
    6,354 reviews,
    70,662 studies,
    744,720 results};

        \node [block, below of=1, node distance=2cm] (12) {
    5,971 reviews,
    66,574 studies,
    705,002 results};

        \node [block, below of=12, node distance=2cm] (13) {
    5,952 reviews,
    65,774 studies,
    632,438 results};

    \node [block, below of=13, node distance=2cm] (2) {
    5,948 reviews,
    65,962 studies,
    695,992 results};

    \node [block, below of=2, node distance=2cm] (3) {
    1,156 reviews,
    26,580 studies,
    175,351 results,
    9,916 meta-analyses};

    \node [block, below of=3, node distance=2cm] (4) {
    1,133 reviews,
    26,101 studies,
    164,222 results,
    9,334 meta-analyses};
